Hamiltonian ABC

### 2015-06-08 draft.tex
Added larger legend overlay

% For figures
\usepackage{graphicx} % more modern
%\usepackage{epsfig} % less modern
%\usepackage{subcaption} 
%usepackage[numers]{natbib}
% For citations
%\usepackage[numbers]{natbib}

@@

% Leave date blank
\date{}

\pagestyle{myheadings}
%\usepackage{sidecap}
%\usepackage[export]{adjustbox}

@@

\begin{figure*}[t]
%\vskip 0.2in
\setlength{\linewidth}{\textwidth}
\setlength{\hsize}{\textwidth}
\begin{center}  
\includegraphics[width=0.65\columnwidth]{./images/exp-SL-MCMC-theta-timeseries-omega-rate-100p0-chain0.pdf}
\includegraphics[width=0.65\columnwidth]{./images/exp-SG-Langevin-theta-timeseries-omega-rate-100p0-chain0.pdf}
\includegraphics[width=0.65\columnwidth]{./images/exponential/exp3-SG-Thermostats-theta-timeseries-omega-rate-100p0-chain0.pdf}
\includegraphics[width=0.65\columnwidth]{./images/exponential/exp2-SL-MCMC-theta-timeseries-omega-rate-0p1-chain3.pdf}
\includegraphics[width=0.65\columnwidth]{./images/exponential/exp2-SG-Langevin-theta-timeseries-omega-rate-0p1-chain3.pdf}
\includegraphics[width=0.65\columnwidth]{./images/exponential/exp2-SG-Thermostats-theta-timeseries-omega-rate-0p1-chain3.pdf}
\vspace{-0.15in}
\caption{\small{Trajectories of the last $1000$ $\thetav$ samples for the demonstration problem.  {\bf Top row:} Non-persistent random seeds.  {\bf Bottom row:} Persistent random seeds with $\gamma = 0.1$.  Each algorithm's parameters were optimized to minimize the total variational distance.  With persistent seeds, each algorithm's random walk behavior is suppressed.  Without persistent seeds, the optimal step-size $\eta$ for SG-Thermostats is small, resulting in an under-dispersed estimate of the posterior; when the seeds are persistent, the gradients are more consistent, and the optimal step-size is larger and therefore there is larger injected noise.  The resulting posteriors are shown in Figure~\ref{fig:exp-posteriors}.
%For SG-Thermostats, persistent $\omegav$ allows for larger $\eta$.Sticky  Explanation thermostats: with no %sticky, need to lower eta, so it shows smoother trajectory.  With sticky, the gradients are more consistent, %allowing for a larger eta and therefore more noise injection.
}}
\label{fig:exp-theta-traces}
\end{center}
\vspace{-0.1in}
\end{figure*}

>>>>

% For figures
\usepackage{graphicx} % more modern
\usepackage{tikz}
%\usepackage{epsfig} % less modern
%\usepackage{subcaption} 
%usepackage[numers]{natbib}
% For citations
%\usepackage[numbers]{natbib}

@@

% Leave date blank
\date{}
\pagenumbering{gobble}
\pagestyle{myheadings}
%\usepackage{sidecap}
%\usepackage[export]{adjustbox}

@@

\begin{figure*}[t]
%\vskip 0.2in
\setlength{\linewidth}{\textwidth}
\setlength{\hsize}{\textwidth}
\begin{center}
\begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) {\includegraphics[width=0.65\columnwidth]{./images/exp-SL-MCMC-theta-timeseries-omega-rate-100p0-chain0.pdf}};
    \node[draw, fill=white] at (4.37, 1.95) {\small SL-MCMC};
\end{tikzpicture}
\begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) {\includegraphics[width=0.65\columnwidth]{./images/exp-SG-Langevin-theta-timeseries-omega-rate-100p0-chain0.pdf}};
    \node[draw, fill=white] at (4.25, 1.93) {\small SG-Langevin};
\end{tikzpicture}
\begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) {\includegraphics[width=0.65\columnwidth]{./images/exponential/exp3-SG-Thermostats-theta-timeseries-omega-rate-100p0-chain0.pdf}};
    \node[draw, fill=white] at (4.06, 1.95) {\small SG-Thermostats};
\end{tikzpicture}
\begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) {\includegraphics[width=0.65\columnwidth]{./images/exponential/exp2-SL-MCMC-theta-timeseries-omega-rate-0p1-chain3.pdf}};
    \node[draw, fill=white] at (4.37, 1.95) {\small SL-MCMC};
\end{tikzpicture}
\begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) {\includegraphics[width=0.65\columnwidth]{./images/exponential/exp2-SG-Langevin-theta-timeseries-omega-rate-0p1-chain3.pdf}};
    \node[draw, fill=white] at (4.25, 1.93) {\small SG-Langevin};
\end{tikzpicture}
\begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) {\includegraphics[width=0.65\columnwidth]{./images/exponential/exp2-SG-Thermostats-theta-timeseries-omega-rate-0p1-chain3.pdf}};
    \node[draw, fill=white] at (4.06, 1.95) {\small SG-Thermostats};
\end{tikzpicture}
%\includegraphics[width=0.65\columnwidth]{./images/exp-SG-Langevin-theta-timeseries-omega-rate-100p0-chain0.pdf}
%\includegraphics[width=0.65\columnwidth]{./images/exponential/exp3-SG-Thermostats-theta-timeseries-omega-rate-100p0-chain0.pdf}
%\includegraphics[width=0.65\columnwidth]{./images/exponential/exp2-SL-MCMC-theta-timeseries-omega-rate-0p1-chain3.pdf}
%\includegraphics[width=0.65\columnwidth]{./images/exponential/exp2-SG-Langevin-theta-timeseries-omega-rate-0p1-chain3.pdf}
%\includegraphics[width=0.65\columnwidth]{./images/exponential/exp2-SG-Thermostats-theta-timeseries-omega-rate-0p1-chain3.pdf}
\vspace{-0.15in}
\caption{\small{Trajectories of the last $1000$ $\thetav$ samples for the demonstration problem.  {\bf Top row:} Non-persistent random seeds.  {\bf Bottom row:} Persistent random seeds with $\gamma = 0.1$.  Each algorithm's parameters were optimized to minimize the total variational distance.  With persistent seeds, each algorithm's random walk behavior is suppressed.  Without persistent seeds, the optimal step-size $\eta$ for SG-Thermostats is small, resulting in an under-dispersed estimate of the posterior; when the seeds are persistent, the gradients are more consistent, and the optimal step-size is larger and therefore there is larger injected noise.  The resulting posteriors are shown in Figure~\ref{fig:exp-posteriors}.
%For SG-Thermostats, persistent $\omegav$ allows for larger $\eta$.Sticky  Explanation thermostats: with no %sticky, need to lower eta, so it shows smoother trajectory.  With sticky, the gradients are more consistent, %allowing for a larger eta and therefore more noise injection.
}}
\label{fig:exp-theta-traces}
\end{center}
\vspace{-0.1in}
\end{figure*}
